Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: comment on robustness of n=0 results

How can we determine the beyond-GR corrections? In GR, comparison between the numerically determined
Kerr QNMs against the fitting formula~\eqref{eq:qnm_nongr_iso} fixes the GR expansion coefficients
$\omega^{(n)}$, $\tau^{(n)}$.
%
We can proceed in a similar way with QNMs calculated in the context of a beyond-GR theory.
%
In particular, in the literature, we can already find fitting formulas relating
the QNMs to the BHs mass, spin and coupling constant $\ell$, the latter being
specific to each theory, up to $n=1$ in the spin expansion (see Table~\ref{tab:ref_theories_qnms}).
%
The idea is then to compare these formulas against Eq.~\eqref{eq:qnm_nongr_iso}
to fix $p$, $\delta\omega^{(n)}$, and $\delta\tau^{(n)}$.

>>>>

How can we determine the beyond-GR corrections? In GR, comparison between the numerically determined
Kerr QNMs against the fitting formula~\eqref{eq:qnm_nongr_iso} fixes the GR expansion coefficients
$\omega^{(n)}$, $\tau^{(n)}$.
%
We can proceed in a similar way with QNMs calculated in the context of a beyond-GR theory.
%
In particular, in the literature, we can already find fitting formulas relating
the QNMs to the BHs mass, spin and coupling constant $\ell$, the latter being
specific to each theory, up to $n=1$ in the spin expansion (see Table~\ref{tab:ref_theories_qnms}).
%
The idea is then to compare these formulas against Eq.~\eqref{eq:qnm_nongr_iso}
to fix $p$, $\delta\omega^{(n)}$, and $\delta\tau^{(n)}$.
%
Because QNMs of rotating BHs in modified gravity theories are not known to
all spin values, we can expect that the $n=1$ coefficients to be susceptible to
changes as calculations beyond-leading order in spin are accomplished.
%
That is not the case for the $n=0$ coefficients and the situation is the same as in GR,
in which the $n=0$ coefficients are simply the QNMs of the Schwarzschild BH.
